Efficient Handling of String-Number Conversion

### 2020-04-05 final-final/evaluation.tex
final version

%	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.

	%	\smallskip

@@

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{PyEx}		& SAT      & 21377& 20350& 18492&  3037 \\
							& UNSAT    &  3860&  3841&  3847&  3816 \\
							& UNKNOWN  &     0&     0&     0&     7 \\
							& TIMEOUT  &   184&  1230&  3082& 16872 \\
							& ERROR    &     0&     0&     0&  1675 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline
%\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
%							& UNSAT    &   286&   214&   100&   111 \\
%							& UNKNOWN  &     0&     0&     0&   345 \\
%							& TIMEOUT  &   188&   335&   487&    89 \\
%							& ERROR    &     0&     0&     0&    20 \\
%							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{LeetCode}	& SAT      &   877&   874&   881&   661 \\
							& UNSAT    &  1785&  1785&  1785&  1780 \\
							& UNKNOWN  &     0&     0&     0&   122 \\
							& TIMEOUT  &    0&    7&     0&    90 \\
							& ERROR    &     4&     0&     0&    13 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{StringFuzz}	& SAT      &   515&   615&   338&   505 \\
							& UNSAT    &   301&   255&   198&   192 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &   249&   195&   529&   364 \\
							& ERROR    &     0&     0&     0&     0 \\
							& INCORRECT&     0&     0&     0&     0 \\\hline
\multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
							& UNSAT    &   822&   818&   808&   774 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &     0&     6&    15&    38 \\
							& ERROR    &     0&     0&     0&     11 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     9&     7&    2 \\
							& UNSAT    &  1032&  1026&  1022&   957 \\
							& UNKNOWN  &     0&     0&     0&     3 \\
							& TIMEOUT  &     3&    10&    16&    58 \\
							& ERROR    &     0&     0&     0&     11 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
\multirow{6}{*}{Total} 		& SAT      & 22792& 21859& 19730&  4213\\
							& UNSAT    &  7800&  7725&  7550&  7519\\
							& UNKNOWN  &     0&     0&     0&   140\\
							& TIMEOUT  &  436&  1448&  3642& 17422 \\
							& ERROR    &     4&     0&     0&  1710\\
							& INCORRECT&     0&     0&     0&    28 \\\hline
\end{tabular}}
\label{table:base_benchmark}}
\end{table}

@@

% \begin{table}[h]
% \centering
% \caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
% \scalebox{0.85}{
% \begin{tabular}{|l r | r r r r |}
% \hline
% \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
% \multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
% 							& UNSAT    &   3854  &  3834 &  3831 &  3836 \\
% 							& $\times$ &   2099  &  1824 &  5062 & 18555 \\ \hline
% \multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
% 							& UNSAT    &    288  &   221 &   100 &   111 \\
% 							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
% \multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
% 							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
% 							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
% \multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
% 							& UNSAT    &    319  &   240 &   186 &   192 \\
% 							& $\times$ &    248  &   154 &   615 &   382 \\\hline
% \multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
% 							& UNSAT    &    820  &   818 &   808 &   772 \\
% 							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
% \multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
% 							& UNSAT    &   1031  &   936 &  1021 &   958 \\
% 							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
% \multirow{3}{*}{Total} 		& SAT      &  21002  & 21517 & 17702 &  4253 \\
% 							& UNSAT    &   8097  &  7834 &  7731 &  7649 \\
% 							& $\times$ &   2533  &  2281 &  6199 & 19730 \\\hline	
% \end{tabular}}
% \label{table:base_benchmark}
% \end{table}

% \begin{table}[h]
% \centering
% \caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
% \scalebox{0.8}{
% \begin{tabular}{|l r | r r r r|}
% \hline
% \multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
% \multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
% 								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
% 								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
% \multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
% 								& UNSAT    &    720  &   660 &   724  &   644 \\
% 								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
% \multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
% 								& UNSAT    &      0  &     0 &     0  &     0 \\
% 								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
% \multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
% 								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
% 								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
% \end{tabular}}
% \label{table:str_int_benchmark}
% \end{table}

@@

%\changed{
%From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
%The second best tool, Z3, fails on 38\% more examples. 
%}
\changed{
From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
The second best tool, Z3, fails on 50 times more examples. 
}
%It fails on twice less cases then Z3, which is ranked the 2nd. In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number. From around 2028 tests generated from this function, around 1000 tests are too difficult for all solvers.  If we exclude the 2028 tests generated from this function, then {\tool} has only $218$ failed cases in total. This is significantly better than the 2nd place tool Z3, which fails on $942$ cases in total.

%We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s. Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3Str3 got almost the same number of failed cases. Z3 also managed to reduce the number of failed cases to 821. %If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.

@@

% \todo{Update table with data of timeout=30s}

% \begin{table}[h]
% \centering
% \caption{Comparison of {\tool}, CVC4, Z3, and Z3Str3 with checkLuhn problems of 2 to 12 loops.}
% \scalebox{0.9}{
% \begin{tabular}{| c | c c c c|}
% \hline
% \# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
% 2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
% 3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
% 4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
% 5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
% 6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
% 7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
% 8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
% 9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
% 10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
% 11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
% 12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
% \end{tabular}}
% \label{table:checkLuhn}
% \end{table}

\hide{
\paragraph{Basic constraint benchmarks.}
This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that were obtained by using an existing tool or generated by other groups. In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in some cases even better.

The first benchmark is called PyEx~\cite{pyex} according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing. This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests. PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints.

The second benchmark is called APLAS that was created by authors of \textsf{$Kepler_{22}$}~\cite{aplas}. The benchmark includes a total of 600 hand-crafted tests (298 satisfiable and 302 unsatisfiable) involving looping word equations (Both sides of the string equality have a common variable) and length constraints over strings.

The next benchmark is called LeetCode~\cite{LeetCode} that was obtained by extracting constraints from Python's testing solutions provided by LeetCode platform. They provide many programming examples and their solutions gathered from technical interviews for companies. Leetcode consists of 881 satisfiable and 1785 unsatisfiable tests that, like PyEx, contain diverse string constraints.

StringFuzz is our next benchmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints. We used StringFuzz to generate 1065 tests including word (dis)equalities, regular membership and arithmetic constraints.

The last two benchmarks, called $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$, are obtained from cvc4 group~\cite{termEQ}. This set of benchmarks consists of the verification of term equivalences over strings and includes various string constraints including string-number and number-string conversion constraints.

\paragraph{String-number conversion constraint benchmarks.}
Our second group of benchmarks was created in order that we could compare our proposed approach for solving string-number and number-string conversions with existing approaches. This group contains a total of 3 benchmarks: full\_str\_int, filtered\_str\_int and rec\_fun. None of these benchmarks were artificially generated but were created from real Python's and javascript's codes.

The first benchmark in the group is full\_str\_int, which is a collection of SMT queries. This collection was generated by applying a tool for concolic testing to Python codes selected from the previously mentioned LeetCode platform and from Python core libraries. All selected Python codes use the \texttt{int()} function, which converts a string into a number system based on the specified base. The Benchmark consists of 21573 tests in total.

The second benchmark, called filtered\_str\_int, is a subset of the previous full\_str\_int benchmark. The filtered\_str\_int benchmark was created by removing tests where cvc4 reported UNSAT and where cvc4's returned unsat core contained no conversion constraint. This benchmark was created in order that we better compare individual conversion approaches. A total of 7396 tests were left.

The last benchmark in the group is rec\_fun, which is a collection of javascript functions that were handcrafted encoded into smt2 format using recursive functions. Besides running examples from the introduction, the benchmark also includes \texttt{split} and \texttt{replaceAll} functions. In total, we managed to create 43 tests that combine several SMT theory and contain conversion constrains.
}

\hide{
In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and Z3Str3 as evauation. To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[]; 
LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[]. Table~\ref{table:base_benchmark} shows the result of the comparison. \changed{The experiments are conducted with a machine of the following specifications: 4-core CPU, 16GB RAM, MacOS 10.15.4.} We set the timeout is to 10 seconds. Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster. The results are either sat, unsat, timeout, or $\times$. In case $\times$, the result may be unknown, error, or exception.

\textbf{Comparison according to Table 1......}

To evaluate our strategy for string-number/number-string conversion, we also prepared a benchmark \texttt{str\_int}\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}. It is collected from two sources of Python programs that use ttexttt{int()} function: Leetcode solutions written in Python and Python core libraries. We concolic tested these Python programs by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs. The SMT queries during the concolic testing are collected as our benchmark. To be more precise in evalutation, we have two versions of \texttt{str\_int} benchmark: \texttt{full\_str\_int} and \texttt{filtered\_str\_int}. \texttt{full\_str\_int} is the original benchmark we collected (i.e. from Python programs using \texttt{int()}); \texttt{filtered\_str\_int} is a subset of \texttt{fill\_str\_int}. We filtered out problems that cvc4 says unsat while the unsat cores do not contain \texttt{str.to.int} or \texttt{int.to.str}. The results of experiment on \texttt{str\_int} benchmark is listed in Table~\ref{table:str_int_benchmark}. The experiments are conducted under the same condition as the experiments on other benchmarks.

\textbf{Comparison according to Table 2.....}
}

\hide{
\begin{table}[]
\caption{Results of z3-Trau, cvc4, and z3 on full\_str\_int benchmark}
\begin{tabular}{|r|r|r|r|r|r|r|}
\hline
Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
z3-Trau		& 3289 & 17089 & 0 & 1195 & 0 & 0 \\ 
cvc4		& 2185 & 16377 & 0 & 3011 & 0 & 0 \\ 
z3seq		& 2716 & 16831 & 0 & 2026 & 0 & 0 \\ 
Z3Str3		& 422 & 16034 & 634 & 4131 & 347 & 5 \\ \hline
\end{tabular}
\label{table:full_str_int}
\end{table}

Table~\ref{table:filtered_str_int} shows the comparison on filtered\_str\_int.  The total amount of cases in filtered\_str\_int is 7396.

\begin{table}[]
\caption{Results of z3-Trau, cvc4, and z3 on filtered\_str\_int benchmark}
\begin{tabular}{|r|r|r|r|r|r|r|}
\hline
Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
z3-Trau		& 3281 & 2912 & 0 & 1203 & 0 & 0 \\ 
cvc4		& 2210 & 2211 & 0 & 2975 & 0 & 0 \\ 
z3seq		& 2729 & 2655 & 0 & 2012 & 0 & 0 \\ 
Z3Str3		& 424 & 1944 & 587 & 4106 & 330 & 5 \\ \hline
\end{tabular}
\label{table:filtered_str_int}
\end{table}
}

\hide{ % keep data of abc and ostrich
\begin{table}[h]
\centering
\caption{Results of Z3-Trau, CVC4, and Z3 on Basic String Constraint benchmarks (numbers with * will be updated later)}
\scalebox{0.7}{
\begin{tabular}{|l r | r r r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18490 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3855 &   3839*  & 3828 & 0 & 871 \\
							& $\times$ &  1977*   &  1824* &  3076 &  18558*  & 2444 & 25421 & 24439 \\ \hline
\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   316 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   206 &    190*  & 339 & 158 & 0 \\
							& $\times$ &   269*   &   148* &   543 &    382*  & 38 & 468 & 1065 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   807 &    772*  & 500 & 443 & 17 \\
							& $\times$ &     5*   &     6* &    16 &     55*  & 88 & 76 & 797 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1020 &    958*  & 596 & 349 & 22 \\
							& $\times$ &     2*   &   101* &    19 &     71*  & 137 & 120 & 978 \\ \hline
\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 2824 & 2205* & 2079 & 1972 & 2079 \\
							& $\times$ & 0* & 0* & 567 & 1186* & 84 & 383 & 13 \\ \hline \hline
\multirow{3}{*}{Total} 		& sat      & * & * & 19724 & * &  &  &  \\
							& unsat    & * & * & 10597 & * &  &  &  \\
							& $\times$ & * & * &  4702 & * &  &  &  \\\hline
\end{tabular}}
\label{table:base_benchmark}
\end{table}
}

\hide{ %3rd version of tables
\begin{table}[t]
	\centering
	\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
	\scalebox{0.7}{
		\begin{tabular}{l r | r r r r}
			\hline
			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3Str3 \\ \hline
			\multirow{3}{*}{String-Number}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
			& unsat    &  17088*  & 16377* & 16832* &  16034* \\
			& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline

				\multirow{3}{*}{leetcode-addStrings}	& sat & 622*  &  330* &  100* &  85* \\ 
				& unsat    &  1054*  & 780* & 1043* &  634* \\
				& $\times$ &  2*  &  568* &  535* & 959* \\ \hline
				\multirow{3}{*}{leetcode-add\_Binary}	& sat & 520*  &  530* &  531* &  11* \\ 
				& unsat    &  1351*  & 1091* & 1091* &  1094* \\
				& $\times$ &  11*  &  261* &  260* & 777* \\ \hline
				\multirow{3}{*}{leetcode-numDecodings}	& sat & 166*  &  107* &  151* &  50* \\ 
				& unsat    &  273*  & 269* & 283* &  269* \\
				& $\times$ &  92*  &  155* &  97* & 212* \\ \hline
				\multirow{3}{*}{leetcode-restoreIpAddresses}	& sat & 811*  &  462* &  864* &  55* \\ 
				& unsat    &  13648*  & 13540* & 13648* &  13342* \\
				& $\times$ &  54*  &  511* &  1* & 1116* \\ \hline
				\multirow{3}{*}{leetcode-validIPAddress}	& sat & 54*  &  57* &  58* &  8* \\ 
				& unsat    &  19*  & 19* & 19* &  19* \\
				& $\times$ &  4*  &  1* &  0* & 50* \\ \hline
				\multirow{3}{*}{leetcode-validWordAbbreviation}	& sat & 183*  &  193* &  188* &  8* \\ 
				& unsat    &  24*  & 11* & 21* &  16* \\
				& $\times$ &  39*  &  42* &  37* & 222* \\ \hline
				\multirow{3}{*}{lib-datetime\_parse\_hh\_mm\_ss\_ff}	& sat &  133*  & 133* &  133* &  88* \\ 
				& unsat    &  41*  & 41* & 41* &  43* \\
				& $\times$ &  0*  &  0* &  0* & 43* \\ \hline
				\multirow{3}{*}{lib-datetime\_parse\_isoformat\_date}	& sat & 32*  &  32* &  32* &  23* \\ 
				& unsat    &  0*  & 0* & 0* &  0* \\
				& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
				\multirow{3}{*}{lib-distutils\_get\_build\_version}	& sat & 19*  &  19* &  19* &  4* \\ 
				& unsat    &  24*  & 24* & 24* &  24* \\
				& $\times$ &  0*  &  0* &  0* & 15* \\ \hline
				\multirow{3}{*}{lib-email\_parsedate\_tz}	& sat & 68*  &  72* &  72* &  30* \\ 
				& unsat    &  138*  & 138* & 138* &  138* \\
				& $\times$ &  4*  &  0* &  0* & 42* \\ \hline
				\multirow{3}{*}{lib-http\_parse\_request}	& sat & 24*  &  24* &  24* &  8* \\ 
				& unsat    &  9*  & 9* & 9* &  7* \\
				& $\times$ &  0*  &  0* &  0* & 18* \\ \hline
				\multirow{3}{*}{lib-ipaddress\_ip\_int\_from\_string}	& sat & 595*  &  204* &  480* &  18* \\ 
				& unsat    &  427*  & 373* & 431* &  357* \\
				& $\times$ &  1006*  &  1451* &  1117* & 1653* \\ \hline
				\multirow{3}{*}{lib-nntplib\_parse\_datetime}	& sat & 4*  &  8* &  0* &  0* \\ 
				& unsat    &  0*  & 0* & 0* &  0* \\
				& $\times$ &  4*  &  0* &  8* & 8* \\ \hline
				\multirow{3}{*}{lib-smtpd\_parseargs}	& sat & 27*  &  27* &  27* &  24* \\ 
				& unsat    &  72*  & 72* & 72* &  66* \\
				& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
				\multirow{3}{*}{lib-wsgiref\_check\_status}	& sat & 10*  &  10* &  10* &  6* \\ 
				& unsat    &  9*  & 9* & 9* &  9* \\
				& $\times$ &  0*  &  0* &  0* & 4* \\ \hline
				% \multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* \\
				% 									& unsat    &   2912*  &  2211* &  2655* &   1944* \\
				% 									& $\times$ &   1203*  &  2975* &  2012* &   5028* \\ \hline
			}
		\end{tabular}
		\label{table:str_int_benchmark}
	\end{table}
}

\hide{  % 2nd version of tables
\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
							& timeout  &  1969*   &     0* &  3211 &  16708*  & 2444 & 0 & 44 \\
							& $\times$ &     8*   &  1824* &     0 &   1850*  & 0 & 25421 & 24395 \\ \hline
\multirow{4}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& timeout  &   185*   &   174* &   481 &     93*  & 386 & 308 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    358*  & 0 & 1 & 599 \\ \hline
\multirow{4}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& timeout  &    26*   &    21* &     0 &     83*  & 15 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    133*  & 46 & 2666 & 890 \\ \hline
\multirow{4}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
							& timeout  &   267*   &    63* &   549 &    377*  & 29 & 297 & 0 \\
							& $\times$ &     2*   &    85* &     0 &      5*  & 9 & 171 & 1065 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
							& timeout  &     5*   &     6* &    15 &     41*  & 23 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &     14*  & 65 & 76 & 797 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
							& timeout  &     2*   &    12* &    17 &     53*  & 50 & 0 & 0 \\
							& $\times$ &     0*   &    89* &     0 &     18*  & 87 & 120 & 978 \\ \hline
\multirow{4}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
							& timeout  & 0* & 0* & 631 & 1186* & 84 & 361 & 9 \\
							& $\times$ & 0* & 0* & 2760 & 0* & 0 & 22 & 4 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                           & {\tool} & CVC4   &    Z3  & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
									& unsat    &  17088*  & 16377* & 16034* &  16832* & 1609 & 0 & 213 \\
									& timeout  &   1191*  &  3011* &  4131* &   2010* & 439 & 0 & 144 \\
									& $\times$ &      0*  &     0* &   986* &      0* & 19367 & 21573 & 21169 \\ \hline
\multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* & 159 & 0 & 47 \\
									& unsat    &   2912*  &  2211* &  2655* &   1944* & 70 & 0 & 0 \\
									& timeout  &   1203*  &  2975* &  2012* &   4106* & 475 & 0 & 119 \\
									& $\times$ &     0*   &     0* &     0* &    922* & 6492 & 7396 & 7230 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}
}

\hide{  % 1st version of tables
\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{Z3Str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19586 & 3858 & 1969/8 & 19763 & 3834 & 0/1824 & 16581 & 3832 & 5008/0 & 3024 & 3839 & 16708/1850 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 38 & 111 & 93/358 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 670 & 1780 &  83/133 \\ 
StringFuzz	& 502 & 294 & 267/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 1021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

>>>>

@@

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{PyEx}		& SAT      & 21377& 20350& 18492&  3037 \\
							& UNSAT    &  3860&  3841&  3847&  3816 \\
							& UNKNOWN  &     0&     0&     0&     7 \\
							& TIMEOUT  &   184&  1230&  3082& 16872 \\
							& ERROR    &     0&     0&     0&  1675 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline
\multirow{6}{*}{LeetCode}	& SAT      &   877&   874&   881&   661 \\
							& UNSAT    &  1785&  1785&  1785&  1780 \\
							& UNKNOWN  &     0&     0&     0&   122 \\
							& TIMEOUT  &    0&    7&     0&    90 \\
							& ERROR    &     4&     0&     0&    13 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{StringFuzz}	& SAT      &   515&   615&   338&   505 \\
							& UNSAT    &   301&   255&   198&   192 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &   249&   195&   529&   364 \\
							& ERROR    &     0&     0&     0&     0 \\
							& INCORRECT&     0&     0&     0&     0 \\\hline
\multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
							& UNSAT    &   822&   818&   808&   774 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &     0&     6&    15&    38 \\
							& ERROR    &     0&     0&     0&     11 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     9&     7&    2 \\
							& UNSAT    &  1032&  1026&  1022&   957 \\
							& UNKNOWN  &     0&     0&     0&     3 \\
							& TIMEOUT  &     3&    10&    16&    58 \\
							& ERROR    &     0&     0&     0&     11 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
\multirow{6}{*}{Total} 		& SAT      & 22792& 21859& 19730&  4213\\
							& UNSAT    &  7800&  7725&  7550&  7519\\
							& UNKNOWN  &     0&     0&     0&   140\\
							& TIMEOUT  &  436&  1448&  3642& 17422 \\
							& ERROR    &     4&     0&     0&  1710\\
							& INCORRECT&     0&     0&     0&    28 \\\hline
\end{tabular}}
\label{table:base_benchmark}}
\end{table}

@@

@@

\changed{
From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
The second best tool, Z3, fails on 50 times more examples. 
}

@@
